HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-16 paper/main.tex
ondrej's comments and fixes

For the annotation of the MT output, we recruited two annotators for each of German, Romanian
and Polish and one main annotator for Czech. In order to allow us to calculate IAA also for
the Czech annotations we recruited several further annotators to work on a small number of 
sentences each. We treat these further annotators as one annotator, giving us two annotators
for each language pair.
The annotators were all native  speakers of the target languages and fluent in English.

In \tabref{tab:annot}
we show the total number of sentences and nodes annotated by each annotator. Note that not all nodes in all sentences were annotated. Sometimes this was because the
annotator did not finish a node, or accidentally missed a node, but in many cases it was also because it was an implicit 
UCCA node, which was not shown to the annotators since there is no corresponding source segment.
\begin{table}
\begin{center}
{\small
\begin{tabular}{ll|cccc}
& & cs & de & pl & ro \\
\hline
Sentences &  Annot. 1 & 324   & 339  & 351  & 230  \\
 & Annot. 2 & 205 & 104  & 340  & 337 \\
\hline
Nodes & Annot. 1 & 8794  & 9253 & 9557  & 6152 \\
 &Annot. 2 & 5553 & 2906  & 9303  & 9228  \\
\end{tabular}
}
\caption{Total numbers of sentences and nodes annotated on the MT output.}
\label{tab:annot}
\end{center}
\end{table}

@@

To calculate Kappa, we consider the annotation task as a classification task on 
nodes, and consider all nodes where there are two annotations from different
annotators We report the overall Kappa, as well as separate Kappas on lexical
nodes (annotated as red, orange or green) and the structural nodes (annotated
as acceptable or bad). In general there should not be confusion between the two
types of nodes, and in future work the separation between the nodes should be enforced
by the tool.  The Kappas are shown in \tabref{tab:iaa}
\begin{table}[!ht]
\begin{center}
\begin{tabular}{l|cccc}
 & cs & de & pl & ro \\
\hline
Sentences & 181 & 102 & 334 & 217 \\
\hline
All nodes & 4686   & 2793   & 8384   & 5604  \\
Kappa & 0.64   & 0.61   & 0.58   & 0.69  \\
\hline
Lexical nodes & 2982 & 1724 & 5386 & 3570 \\
Kappa & 0.54 & 0.29 & 0.54 & 0.50 \\
\hline
Structural nodes & 1602 & 1040 & 2655 & 1989 \\
Kappa & 0.31 & 0.44 & 0.33 & 0.58 \\
\end{tabular}
\caption{Inter-annotator agreement for the multiply-annotated portions of the data, as
measured by Cohen's Kappa. }
\label{tab:iaa}
\end{center}
\end{table}

To assess whether, as we hoped, HUME would make it easier to reliably annotate long sentences,
we binned the sentences according to length and measured Kappa on each of the bins. Each bin covers
a length range of 10, and we show the variance of kappa with length in \figref{fig:iaalength}.

>>>>

For the annotation of the MT output, we recruited two annotators for each of German, Romanian
and Polish and one main annotator for Czech. In order to allow us to calculate IAA also for
the Czech annotations we recruited several further annotators to work on a small number of 
sentences each. We treat these further annotators as one annotator, giving us two annotators
for each language pair.
The annotators were all native  speakers of the respective target languages and fluent in English.

In \tabref{tab:annot},
we show the total number of sentences and nodes annotated by each annotator. Note that not all nodes in all sentences were annotated. Sometimes this was because the
annotator did not finish a node, or accidentally missed a node, but in many cases it was also because it was an implicit 
UCCA node, which was not shown to the annotators since there is no corresponding source segment.
\begin{table}
\begin{center}
{\small
\begin{tabular}{ll|cccc}
& & cs & de & pl & ro \\
\hline
Sentences &  Annot. 1 & 324   & 339  & 351  & 230  \\
 & Annot. 2 & 205 & 104  & 340  & 337 \\
\hline
Nodes & Annot. 1 & 8794  & 9253 & 9557  & 6152 \\
 &Annot. 2 & 5553 & 2906  & 9303  & 9228  \\
\end{tabular}
}
\caption{Total numbers of sentences and nodes annotated on the MT output.}
\label{tab:annot}
\end{center}
\end{table}

@@

To calculate Kappa, we consider the annotation task as a classification task on 
nodes, and consider all nodes where there are two annotations from different
annotators \XXX{unfinished sentence?}
We report the overall Kappa, as well as separate Kappas on lexical
nodes (annotated as red, orange or green) and the structural nodes (annotated
as acceptable or bad). In general there should not be confusion between the two
types of nodes, and in future work the separation between the nodes should be enforced
by the tool.  The Kappas are shown in \tabref{tab:iaa}
\begin{table}[!ht]
\begin{center}
\begin{tabular}{l|cccc}
 & cs & de & pl & ro \\
\hline
Sentences & 181 & 102 & 334 & 217 \\
\hline
All nodes & 4686   & 2793   & 8384   & 5604  \\
Kappa & 0.64   & 0.61   & 0.58   & 0.69  \\
\hline
Lexical nodes & 2982 & 1724 & 5386 & 3570 \\
Kappa & 0.54 & 0.29 & 0.54 & 0.50 \\
\hline
Structural nodes & 1602 & 1040 & 2655 & 1989 \\
Kappa & 0.31 & 0.44 & 0.33 & 0.58 \\
\end{tabular}
\caption{Inter-annotator agreement for the multiply-annotated portions of the data, as
measured by Cohen's Kappa. }
\label{tab:iaa}
\end{center}
\end{table}

To assess whether, as we hoped, HUME would make it easier to reliably annotate long sentences,
we binned the sentences according to length and measured Kappa on each of the bins. Each bin covers
a length range of 10, and we show the variance of kappa with length in \figref{fig:iaalength}.
\XXX{We need to report the number of sentences in each bin, the last German bin
seems to be an unstable result.}
